---
title: 'Data Science - Homework #2'
author: "Jon Brock - JPB2210"
output: 
    github_document:
        toc: TRUE
        toc_depth: 2
---

> *"A man will be imprisoned in a room with a door that's unlocked and opens inwards; as long as it does not occur to him to pull rather than push." - Ludwig Wittgenstein*

```{r load_packages, message = FALSE}
library(tidyverse)
library(readxl)
```

## Problem #1
###### (*25 points*)
##### *Read and clean the Mr. Trash Wheel sheet:*

The following code imports the designated excel file, specifically the sheet named "Mr. Trash Wheel." There is a graphic displayed in the first row of the sheet, so I opted to skip that row when importing. Thereafter, I cleaned the column/variable names by converting them into the ever sexy "snake_case." Then I dropped the column that contained notes. Lastly, I removed all the rows that did not have dumpster-specific data.  

```{r read_in_mr_trash_wheel_data, message = FALSE}
#THIS CODE WORKS! DO NOT CHANGE IT! TAKE OUT THIS MESSAGE WHEN ASSIGNMENT IS COMPLETED!
mr_tw_df <-
    read_excel("./data/HealthyHarborWaterWheelTotals2018-7-28.xlsx", 
               sheet = "Mr. Trash Wheel", skip = 1) %>% 
    janitor::clean_names() %>% 
    select(-x15) %>% 
    drop_na(dumpster)
```

The following code imports the designated excel file, specifically the sheet named "2017 Precipitation." There is no graphic in this sheet, but there is an additional row of header text; I skipped that row when importing. Thereafter, I cleaned the column names as before, removed rows with missing data in the `month` column, and added a new column: `year` with `2017` as its observations.  

```{r read_in_2017_precipitation data, results = FALSE}
#THIS CODE WORKS! DO NOT CHANGE IT! TAKE OUT THIS MESSAGE WHEN ASSIGNMENT IS COMPLETED!
precip_2017 <-
    read_excel("./data/HealthyHarborWaterWheelTotals2018-7-28.xlsx", 
               sheet = "2017 Precipitation", skip = 1) %>%
    janitor::clean_names() %>% 
    drop_na(month) %>% 
    mutate(year = "2017")
```

The following code does everything that the previous code does, with some small changes. The sheet named "2018 Precipitation" was imported, and the addition of the `year` column reflected `2018` as its observations.  

```{r read_in_2018_precipitation data, results = FALSE}
#THIS CODE WORKS! DO NOT CHANGE IT! TAKE OUT THIS MESSAGE WHEN ASSIGNMENT IS COMPLETED!
precip_2018 <-
    read_excel("./data/HealthyHarborWaterWheelTotals2018-7-28.xlsx", 
               sheet = "2018 Precipitation", skip = 1) %>%
    janitor::clean_names() %>% 
    drop_na() %>% 
    mutate(year = "2018")
```

```{r binding_datasets}
precip_17_18 =
    bind_rows(precip_2017, precip_2018)
```


## Problem #2
###### (*25 points*)
##### *Read and Merge 538.com Datasets:*


## Problem #3
###### (*25 points*)
##### *BABY NAMES! BABY NAMES! BABY NAMES!:*