---
title: 'Data Science - Homework #2'
author: "Jon Brock - JPB2210"
output: 
    github_document:
        toc: TRUE
        toc_depth: 2
---

> *"A man will be imprisoned in a room with a door that's unlocked and opens inwards; as long as it does not occur to him to pull rather than push." - Ludwig Wittgenstein*

```{r load_packages, message = FALSE}
library(tidyverse)
library(readxl)
```

## Problem #1
###### (*25 points*)
##### *Read and clean the Mr. Trash Wheel sheet:*

The following code imports the designated excel file, specifically the sheet named "Mr. Trash Wheel." There is a graphic displayed in the first row of the sheet, so I opted to skip that row when importing. Thereafter, I cleaned the column/variable names by converting them into the ever sexy "snake_case." Then I dropped the column that contained notes and removed all the rows that did not have dumpster-specific data. Lastly, I rounded the variable `sports_balls` to the nearest integer and mutated it from a `dbl` to an `int`.

```{r read_in_mr_trash_wheel_data, results = FALSE}
#[COMPLETED] THIS CODE WORKS! DO NOT CHANGE IT! TAKE OUT THIS MESSAGE WHEN ASSIGNMENT IS COMPLETED!
mr_tw_df <-
    read_excel("./data/HealthyHarborWaterWheelTotals2018-7-28.xlsx", 
               sheet = "Mr. Trash Wheel", skip = 1) %>% 
    janitor::clean_names() %>% 
    select(-x15) %>% 
    drop_na(dumpster) %>% 
    mutate(
        sports_balls = as.integer(
            round(sports_balls, digits = 0)))
```

The following code imports the designated excel file, specifically the sheet named "2017 Precipitation." There is no graphic in this sheet, but there is an additional row of header text; I skipped that row when importing. Thereafter, I cleaned the column names as before, removed rows with missing data in the `month` column, and added a new column: `year` with `2017` as its observations.  

```{r read_in_2017_precipitation data, results = FALSE}
#THIS CODE WORKS! DO NOT CHANGE IT! TAKE OUT THIS MESSAGE WHEN ASSIGNMENT IS COMPLETED!
precip_2017 <-
    read_excel("./data/HealthyHarborWaterWheelTotals2018-7-28.xlsx", 
               sheet = "2017 Precipitation", skip = 1) %>%
    janitor::clean_names() %>% 
    drop_na(month) %>% 
    mutate(
        month = month.name[month],
        year = "2017")
```

The following code does everything that the previous code does, with some small changes. The sheet named "2018 Precipitation" was imported, and the addition of the `year` column reflected `2018` as its observations.  

```{r read_in_2018_precipitation data, results = FALSE}
#THIS CODE WORKS! DO NOT CHANGE IT! TAKE OUT THIS MESSAGE WHEN ASSIGNMENT IS COMPLETED!
precip_2018 <-
    read_excel("./data/HealthyHarborWaterWheelTotals2018-7-28.xlsx", 
               sheet = "2018 Precipitation", skip = 1) %>%
    janitor::clean_names() %>% 
    drop_na() %>% 
    mutate(
        month = month.name[month],
        year = "2018")
```

## Problem #2
###### (*25 points*)
##### *Read and Merge 538.com Datasets:*

```{r read_in_three_538_excel_files, results = FALSE}
pols_month <- read_csv("./data/pols-month.csv") #GOOD CODE
unemployment <- read_csv("./data/unemployment.csv") #GOOD CODE
snp <- read_csv("./data/snp.csv") #GOOD CODE
```

```{r clean_pols_month_data}
pols_month %>% #GOOD CODE
    separate(mon, into = (c("year", "month", "day"))) #GOOD CODE %>% 
    #INSERT CODE THAT REPLACES "month" (NUMBER) WITH "month" (NAME) %>% 
    #INSRT CODE THAT:
        #CREATES A NEW COLUMN ("president")
        #CONVERTS "prez_gop" AND "prez_dem" INTO FACTORS(?) WITH "gop" and "dem"
    #INSERT CODE THAT REMOVES "prez_gop", "prez_dem", AND "day"
```

```{r clean_snp_data}
snp %>% #GOOD CODE
    separate(date, into = (c("month", "day", "year"))) %>% #GOOD CODE
    #INSERT CODE THAT REPLACES "month" (NUMBER) WITH "month" (NAME) %>% 
    select(year, month, everything(), -day) #GOOD CODE
```

```{r clean_unemployment_data}
unemployment %>% #GOOD CODE
    janitor::clean_names() %>% #GOOD CODE
    pivot_longer( #GOOD CODE
        jan:dec, #GOOD CODE
        names_to = "month", #GOOD CODE
        values_to = "pct_unemp") %>% #GOOD CODE
    mutate(year = as.character(year))
```

## Problem #3
###### (*25 points*)
##### *BABY NAMES! BABY NAMES! BABY NAMES!:*


```{r}
precip_2017 <-
    read_excel("./data/HealthyHarborWaterWheelTotals2018-7-28.xlsx", 
               sheet = "2017 Precipitation", skip = 1) %>%
    janitor::clean_names() %>% 
    drop_na(month) %>% 
    mutate(
        month = month.name[month],
        year = "2017")
```

